---
title: "Difference in Differences - R Notebook"
output: html_notebook
---


Clean the the R environment.
```{r}
rm(list = ls()) # remove all objects in our R environment
```

Getting sample data.

```{r}
did_data <- read.csv(file = 'DiD_data.csv')
head(did_data)
```

```{r}
# no need to run this if read.csv() works on your computer
#install.packages("readxl") # if you haven't installed this package before
library("readxl")
ab_data <- read_excel(file.choose()) #open the file cookie_cats.xlsx using the menu
head(ab_data)
```


*** Simple Treatment Effect Estimation using DiD ***
Create a dummy variable to indicate the weeks following the treatment launch (i.e., week 53). In this case, weeks before 53 will have a value of 0 and 53+ a 1. If you already have this skip this step.

```{r}
did_data$after = ifelse(did_data$Week >= 53, 1, 0)
```

Create a dummy variable to identify the group exposed to the treatment. In this
example, it is the own brand.

```{r}
did_data$treated = ifelse(did_data$Brand == "Own", 1, 0)
```


```{r}
# Compute for data points for DiD estimation
# Remember: treatment effect = (difference in sales for own brand post-pre) - (difference in sales for competitor post-pre)

# Average sales for the own brand in the post-treatment period
sal_own_af = sapply(subset(did_data, after ==1 & treated == 1, select = Sales), mean)
sal_own_af
```

```{r}
# Average sales for the own brand in the pre-treatment period
sal_own_bef = sapply(subset(did_data, after ==0 & treated == 1, select = Sales), mean)
sal_own_bef
```
```{r}
# Difference in sales for the own brand post-pre

sal_own_dif = sal_own_af-sal_own_bef
sal_own_dif
```


```{r}
# Average sales for the competitor in the post-treatment period
sal_comp_af = sapply(subset(did_data, after ==1 & treated == 0, select = Sales), mean)
sal_comp_af
```

```{r}
# Average sales for the competitor in the pre-treatment period
sal_comp_bef = sapply(subset(did_data, after ==0 & treated == 0, select = Sales), mean)
sal_comp_bef
```
```{r}
# Difference in sales for the competitor post-pre

sal_comp_dif = sal_comp_af-sal_comp_bef
sal_comp_dif
```

```{r}
# Estimate the treatment effect using DiT
treatment_effect = sal_own_dif - sal_comp_dif
treatment_effect

```

*** Treatment Effect Estimation Using DiD and Linear Regression  ***


Create a dummy variable to indicate the weeks following the treatment launch (i.e., week 53). In this case, weeks before 53 will have a value of 0 and 53+ a 1. If you already have this skip this step.

```{r}
did_data$after = ifelse(did_data$Week >= 53, 1, 0)
```

Create a dummy variable to identify the group exposed to the treatment. In this
example, it is the own brand.

```{r}
did_data$treated = ifelse(did_data$Brand == "Own", 1, 0)
```

Create an interaction between time and treated. We will call this ‘DiD’ interaction.

```{r}
did_data$did_int = did_data$after * did_data$treated
```

Estimating the treatment effect using the DiD estimator:

```{r}
did_reg = lm(Sales ~ treated + after + did_int, data = did_data)
summary(did_reg)
```

The coefficient for ‘did_int’ is the difference-in-differences
estimator. It is positive, but insignificant at the 5% level.







